### 2015-05-15 conclusion.tex
fixes

In this paper we presented \whoop, a new fully automatic approach for detecting all possible data races in device drivers. Compared to traditional data race detection techniques that are based on happens-before and typically attempt to explore as many thread interleavings as possible (and thus face code coverage and scalability issues), \textsc{Whoop} uses over-approximation and symbolic pairwise lockset analysis, which has the potential to scale well. Exploiting the race-freedom guarantees provided by \whoop, we showed that we can achieve a sound partial-order reduction that can significantly accelerate \corral, a state-of-the-art concurrent bug-finder. Combining \whoop and \corral, we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution, showing that our technique can analyze drivers 1.5--20$\times$ faster than standalone \corral.

>>>>

In this paper we presented \whoop, a new fully automatic approach for detecting all possible data races in device drivers. Compared to traditional data race detection techniques that are based on happens-before and typically attempt to explore as many thread interleavings as possible (and thus face code coverage and scalability issues), \textsc{Whoop} uses over-approximation and symbolic pairwise lockset analysis, which has the potential to scale well. Exploiting the race-freedom guarantees provided by \whoop, we showed that we can achieve a sound partial-order reduction that can significantly accelerate \corral, a state-of-the-art concurrent bug-finder. Combining \whoop and \corral, we analyzed \sizeOfBenchmarks drivers from the Linux 4.0 kernel, showing that our technique can analyze drivers 1.5--20$\times$ faster than standalone \corral.

### 2015-05-15 evaluation.tex
fixes

We performed experiments to validate the usefulness of the \whoop approach (\S\ref{whoop}) and its combination with \corral (\S\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel distribution.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate race-checking with \corral.

@@

\noindent\textbf{Benchmarks }
%
We evaluate our methodology against \sizeOfBenchmarks drivers from the 4.0 Linux kernel. We chose non-trivial drivers of several types: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. For all these drivers, we had to understand their environment and manually model it; this required approximately two months of work.

>>>>

We performed experiments to validate the usefulness of the \whoop approach (\S\ref{whoop}) and its combination with \corral (\S\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the Linux 4.0 kernel.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate race-checking with \corral.

@@

\noindent\textbf{Benchmarks }
%
We evaluate our methodology against \sizeOfBenchmarks drivers from the Linux 4.0 kernel. We chose non-trivial drivers of several types: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. For all these drivers, we had to understand their environment and manually model it; this required approximately two months of work.
